---
title: "Data Frame Exploration"
output:
  html_document:
    keep_md: yes
    theme: cerulean
    toc: yes
  pdf_document:
    toc: yes
---

## LaTeX Equations in R Markdown

Here is an equation:

$$\alpha = 5 + 2$$

Inline equation: $\alpha = 5 + 2$. 

## Data frame exploration

### Setting up

First, load the `gapminder` R package. If you don't have it installed, run `install.packages("gapminder")` in the console first.

```{r}
library(gapminder)
```

### What is a data frame?

It's tabular data. To get a sense of this, go ahead and print out the `gapminder` object (you might want to do this in the console!).

### Exploration of data frames

Let's explore `gapminder` with functions like `head`, `ncol`, `str`, `summary`.

```{r}
head(gapminder)
str(gapminder)
ncol(gapminder)
summary(gapminder)
```

### Extracting columns/"variables"

Let's extract a column with `$`. Maybe compute its variance.

```{r}
gapminder$pop
```

#### Exploration another data frames mtcars
```{r}
head(mtcars)
str(mtcars)
ncol(mtcars)
summary(mtcars)
```
